Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-05-10 article-models-ttderived.tex
starting to write the dependent logic of extension algebras

\begin{proof}
The proof is a straightforward calculation (start in the middle):
\begin{align*}
\subst{{y_2}{{y_1}{\jcomp{}{e}{f}}}}{{y_0}{f}}
& \jdeq
  \subst{\tmext{y_0}{\subst{y_2}{{y_1}{\jcomp{}{e}{f}}}}}{f}
  \\
& \jdeq
  \subst{{y_2}{{y_1}{{y_0}{\jvcomp{}{\idtm{P}}{\jcomp{}{e}{f}}}}}}{f}
  \\
& \jdeq
  \subst
    {y_2}
    { {y_1}
      { {y_0}
        {\jcomp{}{\jvcomp{}{\idtm{P}}{\jcomp{}{e}{f}}}{f}}
        }
      }
  \\
& \jdeq
  \subst
    {y_2}
    { {y_1}
      { {y_0}
        {\jcomp{}{\jvcomp{}{f}{\idtm{\jcomp{}{f}{{}{e}{P}}}}}{f}}
        }
      }
  \\
& \jdeq
  \subst{{y_2}{{y_1}{{y_0}{\jvcomp{}{f}{\idtm{\jcomp{}{f}{{}{e}{P}}}}}}}}{f}
  \\
& \jdeq
  \subst{\tmext{\subst{y_1}{{y_0}{f}}}{y_2}}{f}
  \\
& \jdeq
  \subst{y_2}{{{y_1}{{y_0}{f}}}{f}}.\qedhere
\end{align*}
\end{proof}

>>>>

\begin{proof}
The proof is a straightforward calculation:
\begin{align*}
\subst{{y_2}{{y_1}{\jcomp{}{e}{f}}}}{{y_0}{f}}
& \jdeq
  \subst{\tmext{y_0}{\subst{y_2}{{y_1}{\jcomp{}{e}{f}}}}}{f}
  \\
& \jdeq
  \subst{{y_2}{{y_1}{{y_0}{\jvcomp{}{\idtm{P}}{\jcomp{}{e}{f}}}}}}{f}
  \\
& \jdeq
  \subst
    {y_2}
    { {y_1}
      { {y_0}
        {\jcomp{}{\jvcomp{}{\idtm{P}}{\jcomp{}{e}{f}}}{f}}
        }
      }
  \\
& \jdeq
  \subst
    {y_2}
    { {y_1}
      { {y_0}
        {\jcomp{}{\jvcomp{}{f}{\idtm{\jcomp{}{f}{{}{e}{P}}}}}{f}}
        }
      }
  \\
& \jdeq
  \subst{{y_2}{{y_1}{{y_0}{\jvcomp{}{f}{\idtm{\jcomp{}{f}{{}{e}{P}}}}}}}}{f}
  \\
& \jdeq
  \subst{\tmext{\subst{y_1}{{y_0}{f}}}{y_2}}{f}
  \\
& \jdeq
  \subst{y_2}{{{y_1}{{y_0}{f}}}{f}}.\qedhere
\end{align*}
\end{proof}

Extension algebras don't come in isolation. There are also extension algebra
families and extension algebra terms. We now aim to define these and to
establish various constructions of new extension algebras out of old ones:
the empty extension algebra, and extensions, weakenings and substitutions
of extension algebras and of course the identity term as an extension algebra
term. We start with extension algebra families.

Consider an extension algebra $\mathcal{A}\defeq(A,P,e,f)$. 
An extension algebra family over $\mathcal{A}$ is likewise a quadruple
$\mathcal{B}\defeq(B,Q,g,h)$. Here we have a family $\jfam{{\Gamma}{A}}{B}$, a
family $\jfam{{{{\Gamma}{A}}{P}}{\jcomp{}{e}{B}}}{Q}$ and
\begin{align*}
\jhom*{{{\Gamma}{A}}{P}}{\ctxext{\jcomp{}{e}{B}}{Q}}{\jcomp{}{e}{B}}{g}\\
\jhom*{{{{\Gamma}{A}}{P}}{\jcomp{}{e}{B}}}{\ctxext{Q}{\jcomp{}{g}{Q}}}{Q}{h}.
\end{align*}
The quadruple $(\jcomp{}{e}{B},Q,g,h)$ is required to be an extension algebra
in context $\ctxext{{\Gamma}{A}}{P}$.

Suppose $\mathcal{A}$ is an extension algebra and $\mathcal{B}$ is an extension
algebra family over $\mathcal{A}$. A term of $\mathcal{B}$ is a pair $(x,y)$
consisting of
\begin{align*}
\jterm*{{\Gamma}{A}}{B}{x}\\
\jterm*{{{\Gamma}{A}}{P}}{\subst{\jcomp{}{e}{x}}{Q}}{y}
\end{align*}
such that... (compatibility of the extensions)
